Probabilities of polar alignment in circumbinary disks

### 2024-12-15 src/tex/ms.tex
Write conclusion

Looking at equation (\ref{eq:Jr}) and equation (3) of \citet{abod2022}, we can write $j$ as
\begin{equation}
    j = \frac{2\pi \Sigma_\text{in} r_\text{in}^{5/2}}{(5/2-p)f(1-f)M_\text{b}\sqrt{a_\text{b}(1-e_\text{b}^2)}}  \left( \left( \frac{r_\text{out}}{r_\text{in}} \right)^{5/2 - p}- 1\right) \, .
\end{equation}

@@

>>>>

Looking at equation (\ref{eq:Jr}) and equation (3) of \citet{abod2022}, we can write $j$ as
\begin{equation}
    \label{eq:j-full-disk}
    j = \frac{2\pi \Sigma_\text{in} r_\text{in}^{5/2}}{(5/2-p)f(1-f)M_\text{b}\sqrt{a_\text{b}(1-e_\text{b}^2)}}  \left( \left( \frac{r_\text{out}}{r_\text{in}} \right)^{5/2 - p}- 1\right) \, .
\end{equation}

@@

In this study we attempt to quantify the fraction of polar disks in circumbinary systems using the dynamics of a thin ring. We do this analytically, numerically in the secular approximation, and numerically using the full binary potential. We find that the three methods produce values of the polar fraction that are identical within their uncertainties.

Our results show that $f_\text{polar}$ is heavily dependent on the underlying parameter distributions that make up a population of systems. There are some populations (e.g. low mass disks around near-circular binaries) where we expect $f_\text{polar}$ to be near zero. Other populations (e.g. low mass disks orbiting binaries with a uniform distribution of $e_\text{b}$) where our results are consistent with previous results from \citet{ceppi2024} which found $f_\text{polar}\sim 0.5$.

Each of the three methods we employ in this paper has its own benefits. With our analytic results, it is possible to compute $f_\text{polar}$ for an arbitrarily large population of systems in less than 1 second. In the same time, our secular numerical method can explore $\sim 50\,000$ combinations of initial conditions for a system, returning relevant timescales and the evolution of orbital parameters for each setup. Our numerical simulations in the full binary potential (using {\sc REBOUND}) are much slower, at $\sim 1/\text{s}$, but allow the inclusion of smaller effects such as those from the binary mass fraction and semi-major axis ratios. Each method balances information output with computational cost.

A fourth method, which we do not consider due to its high cost, would be to run full hydrodynamic simulations of the disk. Such simulations would account for all the additional effects discussed in Section \ref{sec:discussion}, but are not suitable for a large parameter space study. In a detailed study of a particular system our results can be used to gain insight into the dynamics before simulating the full disk. For example, equation (\ref{eq:j-full-disk}) can be used to compute $j$ for a power-law disk, and any of the methods described in Section \ref{sec:analytic}-\ref{sec:reb} can then be used to estimate the dynamical state of the system.

We also discuss the limitations of our methods. First, we look at the effect of finite disk lifetime on the ability for a disk to complete its evolution to a stationary state. Disks with long evolutionary timescales remain with orbital parameters near their initial conditions for their entire lifetimes. We also look at limitations imposed by the fact that real disks are not geometrically thin rings, but have some radial extent. Real disks are likely to break if their radial extent is too large, and will become gravitationally unstable if all of their mass in concentrated in too thin of a ring. These two effects impose constraints on the relationship between $r_\text{in}$, $r_\text{out}$, and $j$.
